---
title: "第四章：Individual geoms"
date: 2020-02-24T22:33:25+08:00
draft: true
author: "北河沿"
type: "post"
categories: 
 - R
 
description: ""
# summary: ""
---

### 这一章节的代码举例：

```{r}
library(ggplot2)
df <- data.frame(
  x = c(3, 1, 5), 
  y = c(2, 4, 6), 
  label = c("a","b","c")
)
p <- ggplot(df, aes(x, y, label = label)) + 
  labs(x = NULL, y = NULL) + # Hide axis label
  theme(plot.title = element_text(size = 12)) # Shrink plot title
```

```{r}
p + geom_point() + ggtitle("point")
```

```{r}
p + geom_text() + ggtitle("text")
```

```{r}
p + geom_bar(stat = "identity") + ggtitle("bar")
```

```{r}
p + geom_tile() + ggtitle("raster")
```

```{r}
p + geom_line() + ggtitle("line")
```

```{r}

p + geom_area() + ggtitle("area")
```

```{r}
p + geom_path() + ggtitle("path")
```

```{r}
p + geom_polygon() + ggtitle("polygon")
```

### 4.1.1 Exercises

1. What geoms would you use to draw each of the following named plots?

Scatterplot

Line chart

Histogram

Bar chart

Pie chart


##### 我的回答

Scatterplot  --> geom_point()

Line chart   --> geom_line()

Histogram   -->geom_histogram()

Bar chart   --> geom_bar(stat = "identity")

Pie chart   --> geom_bar() + coord_polar

##### Pie的例子

###### 第一步
```{r}
# Load ggplot2
# library(ggplot2)

# Create Data
data <- data.frame(
  group=LETTERS[1:5],
  value=c(13,7,9,21,2)
)

# Basic piechart
ggplot(data, aes(x="", y=value, fill=group)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0)
```

###### 改进外观

- 删除数字标签
- 删除格子和背景

```{r}
# Load ggplot2
# library(ggplot2)

# Create Data
data <- data.frame(
  group=LETTERS[1:5],
  value=c(13,7,9,21,2)
)

# Basic piechart
ggplot(data, aes(x="", y=value, fill=group)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  
  theme_void() # remove background, grid, numeric labels
```


#### 添加标签
```{r}
# Load ggplot2
library(ggplot2)
library(dplyr)

# Create Data
data <- data.frame(
  group=LETTERS[1:5],
  value=c(13,7,9,21,2)
)

# Compute the position of labels
data <- data %>% 
  arrange(desc(group)) %>%
  mutate(prop = value / sum(data$value) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )

# Basic piechart
ggplot(data, aes(x="", y=prop, fill=group)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + 
  theme(legend.position="none") +
  
  geom_text(aes(y = ypos, label = group), color = "white", size=6) +
  scale_fill_brewer(palette="Set1")
```


2. What’s the difference between geom_path() and geom_polygon()? What’s the difference between geom_path() and geom_line()?

##### 我的回答：
- geom_polygon() 是在geom_path()之上填充内部。
- geom_path()是按点在数据集中的顺序来连接的，geom_line()则是从左到右连接所有的点。
```{r}
p + geom_line() + ggtitle("line")
```
```{r}
p + geom_path() + ggtitle("path")
```
```{r}
p + geom_polygon() + ggtitle("ploygon")
```

3. What low-level geoms are used to draw geom_smooth()? What about geom_boxplot() and geom_violin()?

##### 我的回答：
- geom_smooth()是用了函数生成了一系列的点，用geom_line(),或geom_path()在做图 参加2.6.1的内容
```{r}
ggplot(mpg, aes(drv, hwy)) + geom_boxplot()
```
- geom_boxplot(), geom_violine()从图形上看，也是geom_path()的运用，数据的计算方式不同。
```{r}
ggplot(mpg, aes(drv, hwy)) + geom_violin()
```







